
---
title: "Lab 5"
author: "Logan Hillers"
date: "2021-02-23"
output: github_document
---
# Question 1
Rename each variable so that it is all lower-case and uses an underscore _ instead of a period . in the name (the recommended coding style in the tidyverse style guide). Print the resulting table.

```{r}

library(tidyverse)

iris <- as_tibble(iris)

iris1 <- rename(iris, sepal_length = Sepal.Length, sepal_width = Sepal.Width, petal_length = Petal.Length, petal_width = Petal.Width, species = Species) 

iris1

```

# Question 2
Convert the four numerical variables from cm to mm by multiplying by 10. Print the resulting table.

```{r}

iris2 <- mutate(iris1, sepal_length = sepal_length * 10, sepal_width = sepal_width * 10, petal_length = petal_length * 10, petal_width = petal_width * 10)

iris2

```

# Question 3
Calculate sepal area and petal area (area is equal to length multiplied by width). Print a table with only the variables sepal area, petal area, and species.

```{r}

iris3.1 <- mutate(iris2, petal_area = petal_width * petal_length, sepal_area = sepal_width * sepal_length)

iris3.2 <- select(iris3.1, -petal_width, -petal_length, -sepal_length, -sepal_width)

iris3.2

```

# Question 4
Calculate the following statistics for the entire dataset from the sepal length variable and print the resulting table:

sample size
maximum value
minimum value
range
median
first quartile (q1)
third quartile (q2)
inter-quartile range (iqr)

```{r}

iris4.1 <- select(iris2, -petal_width, -petal_length, -sepal_width, -species)

iris4.2 <- summarize(iris4.1, mean_length = mean(sepal_length), maximum_length = max(sepal_length), minimum_length = min(sepal_length), range_length = max(sepal_length) - min(sepal_length), median_length = median(sepal_length), first_quantile = quantile(sepal_length, .25), third_quantile = quantile(sepal_length, .75), interquartile_range = IQR(sepal_length))

iris4.2

```

# Question 5
Calculate the following statistics for each species from the petal width variable and print the resulting table:

sample size
mean
standard deviation
variance
standard error of the mean
approximate 95% confidence interval

```{r}

iris5.1 <- select(iris2, -sepal_length, -petal_length, -sepal_width)

iris5.2 <- group_by(iris5.1, species)

iris5.3 <- summarize(iris5.2, sample_size = n(), mean_width = mean(petal_width), standard_deviation = sd(petal_width), variance = var(petal_width), sem = mean(petal_width) / sqrt(sample_size), UCI = mean(petal_width) + (sem * 2), LCI = mean(petal_width) - (sem * 2))

iris5.3

```

# Question 6
Visualize the relationship between petal width and species using a strip plot.

```{r}

iris6.1 <- select(iris3.1, -petal_width, -petal_area, -sepal_area, -sepal_length, -sepal_width)

ggplot(data = iris6.1) +
  geom_jitter(mapping = aes(x = species, y = petal_length), alpha = .1)

```

# Question 7
Starting with the previous graph, add the mean and 95% confidence interval for each species

```{r}

iris7.1 <- select(iris2, -sepal_length, -petal_width, -sepal_width)

iris7.2 <- group_by(iris7.1, species)

iris7.3 <- summarize(iris7.2, sample_size = n(), mean_length = mean(petal_length), standard_deviation = sd(petal_length), variance = var(petal_length), sem = mean(petal_length) / sqrt(sample_size), UCI = mean(petal_length) + (sem * 2), LCI = mean(petal_length) - (sem * 2))

iris7.4 <- select(iris7.3, -sample_size, -standard_deviation, -variance, -sem)

ggplot(data = iris6.1) +
  geom_jitter(mapping = aes(x = species, y = petal_length), alpha = .1) +
  geom_crossbar(
    data = iris7.4, 
    mapping = aes(x = species, y = mean_length, ymax = UCI, ymin = LCI),
    color = "red"
  )

```

# Question 8
Visualize the relationship between petal length, petal width, and species using a scatterplot. Map the two numerical variables to the x and y axes and map species to the color and shape aesthetics.
```{r}

iris8.1 <- select(iris2, -sepal_length, -sepal_width)

ggplot(data = iris8.1) +
  geom_point(mapping = aes(x = petal_width, y = petal_length, color = species))

```

```{r session-info}
sessioninfo::session_info()
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
